% the following command is only required if the thesis is written in german
\RequirePackage[ngerman=ngerman-x-latest]{hyphsubst}

% change to english for english theses
\documentclass[ngerman,BCOR=1.5cm,twoside]{tudscrreprt}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[ngerman]{babel}
\usepackage{isodate}

\usepackage[
    style=numeric-comp,
    backend=biber,
    url=false,
    doi=false,
    isbn=false,
    hyperref,
]{biblatex}
\addbibresource{bibliography.bib}
\AtEveryBibitem{%
    \clearfield{note}%
}

\usepackage[hidelinks]{hyperref} % makes all links clickable but hides ugly boxes
\usepackage[capitalise,nameinlink,noabbrev]{cleveref} % automatically inserts Fig. X in the text with \cref{..}

\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

\usepackage{graphicx}
\graphicspath{ {./images/} }

% if you need mathy stuff
\newtheorem{lem}{Lemma}
\crefname{lem}{Lemma}{Lemmas}
\newtheorem{thm}{Theorem}
\crefname{thm}{Theorem}{Theorems}
\newtheorem{defs}{Definition}
\crefname{defs}{Def.}{Defs.}

\usepackage{blindtext}

%\usepackage{tudscrsupervisor} % if you want to copy the sources of the task description into the thesis

\usepackage{csquotes}



\usepackage{caption}
\captionsetup{font=sf,labelfont=bf,labelsep=space}
\usepackage{floatrow}
\floatsetup{font=sf}
\floatsetup[table]{style=plaintop}
\captionsetup{singlelinecheck=off,format=hang,justification=raggedright}
\DeclareCaptionSubType[alph]{figure}
\DeclareCaptionSubType[alph]{table}
\captionsetup[subfloat]{labelformat=brace,list=off}

\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{tabulary}
\usepackage{tabu}
\usepackage{longtable}

\usepackage{quoting}

\usepackage[babel]{microtype}

\usepackage{xfrac}

\usepackage{enumitem}
\setlist[itemize]{noitemsep}

\usepackage{ellipsis}
\let\ellipsispunctuation\relax

\input{lst.tex}

\begin{document}

\faculty{Fakultät Informatik}
\department{}
\institute{Institut für Software- und Multimediatechnik}
\chair{Lehrstuhl für Softwaretechnologie}
\title{%
    Entwicklung eines optimalen Verfahrens zur Eroberung des
    Geldspeichers in Entenhausen
}

%% for a bachelor thesis
%\thesis{bachelor}
%\graduation[B.Sc.]{Bachelor of Science}

% for a master thesis
\thesis{master}
\graduation[M.Sc.]{Master of Science}

% for a diploma thesis
%\thesis{diploma}
%\graduation[Dipl.Inf.]{Diplom-Informatiker}

\author{Mickey Mouse}
\emailaddress[]{mickey.mouse@tu-dresden.de}
\matriculationnumber{12345678}
\matriculationyear{2016}
\dateofbirth{1.1.1990}
\placeofbirth{Dresden}
%\discipline{Distributed Systems Engineering}

\course{Distributed Systems Engineering}

\supervisor{%
    Dipl.-Inf. ABC XYZ%
    \and Dr. Sebastian Götz%
}
\professor{Prof. Dr. rer. nat habil. Uwe Aßmann}
\date{10.10.2018}
\maketitle
\newpage

\tableofcontents
\listoffigures
\listoftables

\input{sections/einleitung}
\input{sections/grundlagen.tex}
\input{sections/problem.tex}
\input{sections/eval.tex}
\input{sections/zusammenfassung.tex}

\printbibliography[heading=bibintoc]\label{sec:bibliography}%

\appendix
\input{sections/appendix}

\confirmation

\end{document}
